Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-19 talk/pepm2011/paper.tex
fixes

To optimize the trace, it is traversed from beginning to end. Every
optimization in the input trace is either removed, or new operations are
produced. Whenever a \lstinline{new} operation is seen, the operation it is
removed optimistically and a \emph{static object}\footnote{Here ``static'' is
meant in the sense of partial evaluation, \ie known at partial evaluation time,
not in the sense of static allocation or static method.} is constructed and
associated with the result variable. The static object describes the shape of
the original object, \ie where the values that would be stored in the fields of
the allocated object come from, as well as the type of the object.

When a \lstinline{set} that writes into a static object is optimized, the
corresponding shape description is updated and the operation is removed. This
means that the operation was done at partial evaluation time. When the
optimizer encounters a \lstinline{get} from a static object, the result is read
from the shape description, and the operation is also removed. Equivalently, a
\lstinline{guard_class} on a variable that has a shape description can be
removed as well, because the shape description stores the type and thus the
outcome of the type check the guard does is statically known. Operations that
have dynamic (\ie all other) objects as arguments are just left untouched by
the optimizer.

>>>>

To optimize the trace, it is traversed from beginning to end. Every
operation in the input trace is either removed, or new operations are
produced. Whenever a \lstinline{new} operation is seen, the operation it is
removed optimistically and a \emph{static object}\footnote{Here ``static'' is
meant in the sense of partial evaluation, \ie known at partial evaluation time,
not in the sense of static allocation or static method.} is constructed and
associated with the result variable. The static object describes the shape of
the original object, \ie where the values that would be stored in the fields of
the allocated object come from, as well as the type of the object.

When a \lstinline{set} that writes into a static object is optimized, the
corresponding shape description is updated and the operation is removed. This
means that the operation was done at partial evaluation time. When the
optimizer encounters a \lstinline{get} from a static object, the result is read
from the shape description, and the operation is also removed. Equivalently, a
\lstinline{guard_class} on a variable that has a shape description can be
removed as well, because the shape description stores the type and thus the
outcome of the type check the guard does is statically known. Operations that
have dynamic (\ie non-static) objects as arguments are just left untouched by
the optimizer.
